---
title: "meanwhile"

#Get file and load libraries
```{r,results="hide"}
path<- getwd()
file.path(path, "repdata_data_activity")
data<- unzip(zipfile =  "repdata_data_activity.zip")
data1<- read.csv(data)
library(dplyr)
library(ggplot2)
```
# Organize data
```{r, results="hide"}
data1<- read.table(data, skip = 1, sep=",")
names(data1)<-c("steps", "date", "interval")
as.Date(data1$date)
```

# group steps by date and do a function with the mean steps
```{r}
stepsperday<- data1 %>%
  group_by(date)%>%
  summarise(sumsteps=sum(steps, na.rm = T))
```
# Make histogram and get the mean and the median
```{r}
hist(stepsperday$sumsteps, freq = T, col="green", main = "Daily steps per day", xlab = "Total steps")
mean<- round(mean(stepsperday$sumsteps))
median<- round(median(stepsperday$sumsteps))
```

#Group average per interval
```{r}
databyinterval <- data1%>% 
  select(interval, steps) %>% 
  na.omit() %>% 
  group_by(interval) %>% summarize(sumsteps= mean(steps))
```
##Time series plot
```{r}
ggplot(databyinterval, aes(x=interval, y=sumsteps))+ geom_line()+ ylab("average steps")+ xlab("5 minutes interval") + ggtitle("Average steps per 5 minute interval")

databyinterval[which(databyinterval$sumsteps== max(databyinterval$sumsteps)),]
```
#replace missing values and check the data
```{r, results="hide"}
missing_values<- sum(is.na(data1))
replacena <- function(x)replace(x, is.na(x), mean(x, na.rm=T))
meandata<- data1%>% group_by(interval) %>% mutate(steps= replacena(steps))
is.na(meandata)
```
#Data in steps per day 
```{r}
stepsPerDay1 <- meandata %>%
  group_by(date) %>%
  summarize(sumsteps = sum(steps, na.rm = TRUE))
```
# Histogram of total steps per day whithout NA
## In the lower spectrum of steps there is a great change, the mean changes for about a thousand 
```{r}
hist(stepsPerDay1$sumsteps, freq = T, col="green", main = "Daily steps per day", xlab = "Total steps")
mean1<- round(mean(stepsPerDay1$sumsteps))
median1<- round(median(stepsPerDay1$sumsteps))
mean1
median1
```
# Differences in activity patterns between weekdays and weekends
```{r}
meandata$date <- as.Date(meandata$date)
meandata$weekday <- weekdays(meandata$date)
meandata$weekend <- ifelse(meandata$weekday=="sabado" | meandata$weekday=="domingo", "Weekend", "Weekday" )


ggplot(meandata, aes(x=interval, y=steps, color=weekend)) + geom_line()+
  facet_grid(weekend ~.) + xlab("Interval") + ylab("Average Steps") +
  ggtitle("Average Number of Steps in Weekends vs Weekdays")
```